### 2017-01-11 main.tex
Add birds B, C, D to Quantification section. Add dataset sizes in a table.

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on a few others.  For
simplicity, and to test robustness to imperfect choice of ``syllable'', we present performance on 6 randomly chosen points in one
bird's song.  The results presented here are representative of
real-world performance over many birds in our lab.

We divided the data into training and test sets.  For the results
reported in the following section, the training set consisted of 1000
instances of the song of one bird, and 2000 song-length samples of
non-song (cage noise, calls, other birds' song).  Our test set
consisted of an additional 1818 iterations of the bird's song and 3636
song-length samples of non-song.

>>>>

We measure accuracy and characterise timing for 6 randomly chosen
points in one bird's song (Bird A), and present accuracy results for
three more birds (B, C, D) (timing does not appreciably vary among
birds). The results presented here are representative of real-world
performance in feedback experiments on many birds in our lab.

% A:
% B: LNY46 0.28s
% C: LNY42 0.38s
% D: LNY4RB 0.25s

Data consisted of extracted, aligned songs, and additional song-length samples of non-song (cage noise, calls, other birds' song). These were divided into training and test sets. The sizes of our data sets are given in Table~\ref{table:datasizes}.

\begin{table}
  \begin{tabular}{c|cccc}
    Bird & Training songs & Test songs & Training non-song & Test non-song \\ \hline
    A & 1000 & 1818 & 1000 & 3636 \\
    B & 1000 & 1533 & 158 & 242 \\
    C & 1000 & 1245 & 178 & 222 \\
    D & 1000 & 1614 & 153 & 247
  \end{tabular}
  \caption{Sizes of our training and test sets.}
  \label{table:datasizes}
\end{table}
